\tool: Revisiting BadUSB with Type-C

### 2021-01-26 WOOT/Files/related_work.tex
fix JFCGuard
Figures

In addition to injection attacks, data theft attack is also one of the focuses of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim. In order to mitigate this issue, Meng et al.\cite{JFC} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.

@@

		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{JFCGuard\cite{JFC}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull  \@ means that the defense is effective
	\item[2] \circlehalf \@ means that the defense is partial effective
	\item[3] \circleempty \@  means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}

>>>>

In addition to injection attacks, data theft attack is also one of the focuses of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim. In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.

@@

		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{JFCGuard\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull  \@ means that the defense is effective
	\item[2] \circlehalf \@ means that the defense is partial effective
	\item[3] \circleempty \@  means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of Defense against Different Attacks}
	\label{table:attack_vs_defense}
\end{table*}
